Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-26 writeup/parkinsons.tex
Only remove NAs from interpreted features
This makes the number of data points rise from 781 to 901 participants.

Will need to rerun all figures and recalculate statistics, so I pushed
a tag up. Get ready!

\subsection{Dataset Description}
951 subjects, 145 metrics, collected 15-4-2012. From Pablo Martinez Mart\'in.
170 subjects with missing values (brought down to 781); these were removed
automatically, even if the missing values were not included in the selected
features below. This will need to be changed later on, by keeping those
removed that still have all selected features and perhaps with some
compensation for missing values.

>>>>

\subsection{Dataset Description}
951 subjects, 145 metrics, collected 15-4-2012 from Pablo Martinez \'in. Only
19 features used for clustering and/or interpretation.  50 subjects with
missing values of the features to be used in clustering (brought down to 901).
Imputation may be a good idea later on.
